---
title: "Prototype Flexdashboard"
author:
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

<style>
.navbar {
  margin: 0;
  padding: 0;
  height: 100%;
  display: block;
  position: fixed;
  width: 200px; /* Modify the width of the sidebar */
}
body {
          margin-left: 200px; /* Add a left margin to avoid content     overlay */
padding-top:0px
}
</style>

```{r setup, include=FALSE}
library(flexdashboard)

# LIBRARY AND PACKAGES ---------------------------------------------------------
.libPaths("C:/R library")
getwd()

# for general formatting
if(!require("tidyverse")) {install.packages("tidyverse")}
library(tidyverse)
library(magrittr)
if(!require("readxl")) {install.packages("readxl")}
library(readxl)

# for theme trees
if(!require("visNetwork")) {install.packages("visNetwork")}
library(visNetwork)

# for plotting text and wordclouds
if(!require("kableExtra")) {install.packages("kableExtra")}
library(kableExtra)
if(!require("tidytext")) {install.packages("tidytext")}
library(tidytext)
if(!require("wordcloud")) {install.packages("wordcloud")}
library(wordcloud)

```

 
# Abstract

### Authors {data-height=100}
Author names or project citation here

### Context and Aims {data-height=225}
Outline context and aims here

### Method {data-height=225}
Outline method briefly here (supported by separate technical documents)

### Results {data-height=225}
Direct reader to seperate sections of the Flexdashboard

### Implications {data-height=225}
Outline concise conclusions and implications from the results



# Results {data-navmenu="Quant Overview" data-icon="fa-signal"}

## Column {data-width=200}

### Notes
```{r}
print("add notes here")
```

## Column {data-width=250}

### Chart A1
```{r}
print("add summary visual")
```

### Chart A2
```{r}
print("add summary visual")
```

## Column {data-width=500}

### Chart B
```{r}
print("add summary visual")
```



# Theme Tree {data-navmenu="Qual Overview" data-icon="fa-tree"}

### Qual Theme Overview
```{r}
# DIAGONAL NETWORK VISUALIATION ------------------------------------------------
# with visNetwork package

visNodes <- read_xlsx("visNodes.xlsx")
visEdges <- read_xlsx("visEdges.xlsx")

#increase fontsize of nodes
visNodes <-
  visNodes %>%
  mutate(font.size = 30) %>%
  mutate(shape = 'rectangle')

visNetwork(visNodes, visEdges) %>%
  visNodes() %>%
  visEdges(arrows = "to") %>%
  visHierarchicalLayout(direction = "LR", levelSeparation = 500) %>%
  visOptions(collapse = TRUE)

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# 2) IMPORT NVIVO CODING MATRIX ------------------------------------------------

# Next we read in the Framework Matrix to provide more detailed visuals on the 
# parent and child themes. 

# read in Nvivo theme coding matrix
Nvivo_themes <- read_excel("NVivo Output 2 - Framework Matrix.xlsx") # may have
# resave this in Excel (as .xlsx) if NVivo kicks out bad encoding.

# split nvivo ID from main ID and drop nvivo ID
Nvivo_themes <- separate(data = Nvivo_themes, 
                         col = ...1, 
                         into = c("nvivoID", "ID"), 
                         sep = ":")

Nvivo_themes %<>%
  select(-nvivoID) # drop Nvivo ID

# formatting the new df
Nvivo_themes$ID <- as.numeric(Nvivo_themes$ID)
Nvivo_themes <- Nvivo_themes[order(Nvivo_themes$ID), ]
Nvivo_themes <- as.data.frame(Nvivo_themes)

# specific formatting for dataset (optional extra parameters)
Nvivo_themes <- Nvivo_themes[,-c(7)]
Nvivo_themes <- Nvivo_themes[,-c(14:25)]

# If mixed methods - join nvivo themes to main df
#<full_data> <- left_join(<full_data>, Nvivo_themes, by = "ID")

# THEME COUNTS -----------------------------------------------------------------

# code block to take total persons who mentioned each theme (not references)

# function to count text strings in each column
theme_counter <- function(x) {
  length(which(str_detect(x, pattern = "")))
}

# apply function across each column in df and return counts as values
theme_counts <- apply(Nvivo_themes, MARGIN = 2, FUN = theme_counter)
theme_counts <- data.frame(theme_counts)

# set up new df with themes as a first column and counts as second column
col_names <- list(colnames(Nvivo_themes)) # list theme names
theme_total <- data.frame(col_names, theme_counts)
rownames(theme_total) <- NULL # get rid of rownames from before
theme_total %<>%
  rename("theme" = c..ID....A...Issues....B...Heavy....C...Misrepresented.Child.weight...) %>%
  mutate(theme = as.factor(theme)) %>%
  mutate(theme_counts = as.numeric(theme_counts))

rm(col_names, theme_counts)
```


# Issues {data-navmenu="Qual Overview" data-icon="fa-list"}

## Overview {data-height=400}

[This would be an overview of parent theme].

## Sub-theme prevalence {data-height=600}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# PLOT THEME DATA --------------------------------------------------------------
theme_total[3:5, ] %>%
  ggplot(aes(x = theme, y = theme_counts)) +
  geom_col(fill = "#0390fc") +
  coord_flip() +
  theme_bw() +
  scale_y_continuous(breaks = 0:25)

```

# NA Reviews {data-navmenu="Qual Overview" data-icon="fa-list"}

## Overview {data-height=400}

[This would be an overview of parent theme].

## Sub-theme prevalence {data-height=600}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# PLOT THEME DATA --------------------------------------------------------------
theme_total[6, ] %>%
  ggplot(aes(x = theme, y = theme_counts)) +
  geom_col(fill = "#0390fc") +
  coord_flip() +
  theme_bw() +
  scale_y_continuous(breaks = 0:25)
  
```

# Positive Views {data-navmenu="Qual Overview" data-icon="fa-list"}

## Overview {data-height=400}

[This would be an overview of parent theme].

## Sub-theme prevalence {data-height=600}

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# PLOT THEME DATA --------------------------------------------------------------
theme_total[7:13, ] %>%
  ggplot(aes(x = theme, y = theme_counts)) +
  geom_col(fill = "#0390fc") +
  coord_flip() +
  theme_bw() +
  scale_y_continuous(breaks = 0:25)

```




# Issues > Heavy {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`B : Heavy` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()

```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`B : Heavy` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  #anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```


# Issues > Misrepresented child weight {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`C : Misrepresented Child weight` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`C : Misrepresented Child weight` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```


# Issues > Rain cover {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`D : Rain cover` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`D : Rain cover` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```

# NA review {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`E : NA review` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`E : NA review` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```

# Positive view > Child enjoys {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`G : Child enjoys` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()

```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`G : Child enjoys` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  #anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```


# Positive view > Compact {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`H : Compact` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`H : Compact` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```


# Positive view > Easy to use {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`I : Easy to use` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`I : Easy to use` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```

# Positive view > General view {data-navmenu="Qual Detailed" data-icon="fa-list"}

## Overview 

[This would be an overview of sub theme]

## plot quotes
```{r}
# plot quotes
Nvivo_themes$`J : General view` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  rename("Example Quotes" = ".") %>%
  kbl() %>%
  kable_styling()
```

## plot wordcloud
```{r}
# plot wordcloud
Nvivo_themes$`J : General view` %>% # change for each child theme
  na.omit() %>%
  as.data.frame() %>%
  unnest_tokens(word, ".") %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100, min.freq = 1))
```